Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-03-29 analyses/reproduce_analyses.Rmd
reset bootstraps to 1000 for statistical inferences.
added code to calculate curvature. the problem is that bootstrapped gammas and betas are estimated from different models, so bootstrap i for the gammas doesn't correspond to bootstrap i for the betas. I'm going to start a branch that alters upstream code to implement poly(x,2) so I can estimate linear (betas) and nonlinear terms (gammas) within the same model.

```{r set parameters}
# Number of bootstrap replicates
n_boots_analysis <- 100
n_boots_plots <- 100

@@

>>>>

```{r set parameters}
# Number of bootstrap replicates
n_boots_analysis <- 1000
n_boots_plots <- 100

@@

```{r Curvature, echo=FALSE}
# Calculate curvatures for complex food web
foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)

# Calculate curvatures for simple food web
foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)

# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_curvs <- bind_cols(foodweb_complex_raw_curvs, foodweb_simple_raw_curvs) %>%
  mutate(`FoodwebDiff:C.Diam` = `FoodwebSimple:C.Diam` - `FoodwebComplex:C.Diam`,
         `FoodwebDiff:C.Clutch` = `FoodwebSimple:C.Clutch` - `FoodwebComplex:C.Clutch`,
         `FoodwebDiff:C.Pref` = `FoodwebSimple:C.Pref` - `FoodwebComplex:C.Pref`,
         `FoodwebDiff:C.Diam:Clutch` = `FoodwebSimple:C.Diam:Clutch` - `FoodwebComplex:C.Diam:Clutch`,
         `FoodwebDiff:C.Diam:Pref` = `FoodwebSimple:C.Diam:Pref` - `FoodwebComplex:C.Diam:Pref`,
         `FoodwebDiff:C.Clutch:Pref` = `FoodwebSimple:C.Clutch:Pref` - `FoodwebComplex:C.Clutch:Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_foodweb_curvs <- foodweb_curvs %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

```{r Table of food web curvatures, echo=FALSE}
tidy_foodweb_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
```

```{r Table of differences in curvatures between food-web treatments, echo=FALSE}
tidy_foodweb_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
```
